---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo <- FALSE,  # don't print the code chunk
  warning <- FALSE,  # don't print warnings
  message <- FALSE,  # don't print messages
  fig.width <- 5,  # set default width of figures
  fig.height <- 8,  # set default height of figures
  fig.align <- "center",  # always align figure in center
  fig.pos <- "H",  # always plot figure at the exact location of the code chunk
  cache <- FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)

## hand written functions ##
source(path(here(), "R", "load_behave_data.R"))
source(path(here(), "R", "prep_behave_data.R"))
source(path(here(), "R", "stretch_start_end.R"))
source(path(here(), "R", "load_high_gamma_data.R"))
source(path(here(), "R", "rolling_window_and_baseline.R"))
source(path(here(), "R", "run_permuted_regressions_par.R"))
source(path(here(), "R", "compile_mult_reg_results.R"))
source(path(here(), "R", "run_filtered_anova.R"))
source(path(here(), "R", "merge_stepped_anova_results.R"))
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'load_interaction_results_and_combine.R'))
source(path(here(), "R", "load_and_collate_reg_results.R"))

## plotting helpers ##
ggthemr("solarized")
getPalette = colorRampPalette(brewer.pal(9, "Set1"))

## parallelization ##
nCores <- 2
registerDoParallel(nCores)

```



okay HERE is the plan

take the electrodes that are in the ofc that are significant for dis inequity (or inequity in general?)
look at the multiple regressions and see if you can deduce what is going on by looking at the beta weights

then try ming plan on a subset of those


```{r create-ineq_disadvent-dfs}
# load results for self var #
ineq_disadvent_results_pres <- load_and_collate_reg_results(tag = "ineq_disadvent_theta-pres-locked-hilbertRS", epoch = "presentation", folder = "post_eda")
ineq_disadvent_results_choice <- load_and_collate_reg_results(tag = "ineq_disadvent_theta-choice-locked-hilbertRS", epoch = "choice", folder = "post_eda")

# change predictor #
ineq_disadvent_results_pres <- ineq_disadvent_results_pres %>% mutate(predictor = "ineq_disadvent") %>% mutate(type = "single")
ineq_disadvent_results_choice <- ineq_disadvent_results_choice %>% mutate(predictor = "ineq_disadvent") %>% mutate(type = "single")

```

```{r create-self-payoff-dfs}
# load results for self var #
self_var_results_pres <- load_and_collate_reg_results("self_var_payoff_theta-pres-locked-hilbertRS", epoch = "presentation", folder = "post_eda")
self_var_results_choice <- load_and_collate_reg_results("self_var_payoff_theta-choice-locked-hilbertRS", epoch = "choice", folder = "post_eda")

# change predictor #
self_var_results_pres <- self_var_results_pres %>% mutate(predictor = "self_var_payoff") %>% mutate(type = "single")
self_var_results_choice <- self_var_results_choice %>% mutate(predictor = "self_var_payoff") %>% mutate(type = "single")

```

```{r create-self-payoff-adv-dfs}
# load results for self var #
self_var_adv_results_pres <- load_and_collate_reg_results("self_var_payoff_adv_theta-pres-locked-hilbertRS", epoch = "presentation", folder = "post_eda")

# change predictor #
self_var_adv_results_pres <- self_var_adv_results_pres %>% mutate(predictor = "self_var_payoff_adv") %>% mutate(type = "single")

```

```{r create-trial-type-dfs}
# load results for self var #
trial_type_results_pres <- load_and_collate_reg_results("trial_type_theta-pres-locked-hilbertRS", epoch = "presentation", folder = "post_eda")

# change predictor #
trial_type_results_pres <- trial_type_results_pres %>% mutate(predictor = "trial_type") %>% mutate(type = "single")

```

```{r create-self-payoff-dis-dfs}
# load results for self var #
self_var_dis_results_pres <- load_and_collate_reg_results("self_var_payoff_dis_theta-pres-locked-hilbertRS", epoch = "presentation", folder = "post_eda")

# change predictor #
self_var_dis_results_pres <- self_var_dis_results_pres %>% mutate(predictor = "self_var_payoff_dis") %>% mutate(type = "single")

```

```{r create-other-payoff-dfs}
# load results for self var #
other_var_results_pres <- load_and_collate_reg_results(tag = "other_var_payoff_theta-pres-locked-hilbertRS", epoch = "presentation", folder = "post_eda")
other_var_results_choice <- load_and_collate_reg_results(tag = "other_var_payoff_theta-choice-locked-hilbertRS", epoch = "choice", folder = "post_eda")

# change predictor #
other_var_results_pres <- other_var_results_pres %>% mutate(predictor = "other_var_payoff") %>% mutate(type = "single")
other_var_results_choice <- other_var_results_choice %>% mutate(predictor = "other_var_payoff") %>% mutate(type = "single")

```


```{r create-pie-size-dfs}
# load results for self var #
pie_size_results_pres <- load_and_collate_reg_results(tag = "pie_size_theta-pres-locked-hilbertRS", epoch = "presentation", folder = "post_eda")

# change predictor #
pie_size_results_pres <- pie_size_results_pres %>% mutate(predictor = "pie_size") %>% mutate(type = "single")

```



```{r localization-data}

merge_all_subs_with_elec_info <- function(df, localizations) {
## merge df with elec info, stored in localizations
## creates new var of form ROI1-ROI2  
## also cleans elec names
  
  # only the localization columns we need #
  localizations <- localizations %>% select(Electrode, subject, `Loc Meeting`)
  
  # clean the names
  df <- df %>%
    mutate(electrode = gsub("POL ", "", electrode)) %>%
    mutate(electrode = gsub(" POL", "", electrode)) %>%
    mutate(electrode = gsub("-Ref", "", electrode)) %>%
    mutate(electrode = gsub("-Ref-", "-", electrode)) 
  
  # separate two electrodes
  df <- df %>%
    mutate(first_elec= gsub("-.*", "", electrode)) %>%
    mutate(second_elec = gsub(".*-", "", electrode))
  # join on first electrode
  df <- left_join(df,
                 localizations,
                 by = c("sub" = "subject", "first_elec" = "Electrode"))
  # rename to `first_region`
  df <- df %>%
    rename(first_region = `Loc Meeting`)
  # join on second electrode and rename
  df <-  left_join(df,
             localizations,
             by = c("sub" = "subject", "second_elec" = "Electrode")) %>%
    rename(second_region = `Loc Meeting`) 
  # paste into useful format
  df <- df %>% mutate(ROI = paste0(first_region, "-", second_region))
  
  return(df)

}

# read in raw localizations data #
localizations <- read_csv(path(here(), "munge", "combined_electrode_info_with_bob.csv"))
ineq_disadvent_localized_results_pres <- merge_all_subs_with_elec_info(ineq_disadvent_results_pres, localizations)

# significant and ofc electrodes only 
ofc_electrodes_of_interest <- ineq_disadvent_localized_results_pres %>% 
  filter(grepl("ofc", ROI, ignore.case = T) | grepl("orbit", ROI, ignore.case = T)) %>% 
  filter(perm_p < 0.05)

ofc_non_sig_electrodes_of_interest <- ineq_disadvent_localized_results_pres %>% 
  filter(grepl("ofc", ROI, ignore.case = T) | grepl("orbit", ROI, ignore.case = T)) %>% 
  filter(perm_p >= 0.05)


```

```{r merge-with-other-single-regs}

## subset only perm p and merging columns of other main regressors, rename for table view ##
# self var payoff #
self_var_results_pres_short <- self_var_results_pres %>% 
  rename(self_only = perm_p) %>%
  select(sub, electrode, self_only)
# other var payoff #  
other_var_results_pres_short <- other_var_results_pres %>% 
  rename(other_only = perm_p) %>%
  select(sub, electrode, other_only)
# other var payoff #  
pie_size_results_pres_short <- pie_size_results_pres %>% 
  rename(pie_size = perm_p) %>%
  select(sub, electrode, pie_size)
  
## merge with ofc elecs of interest #  
ofc_all_sing_regs <- left_join(ofc_electrodes_of_interest, self_var_results_pres_short)

ofc_all_sing_regs <- left_join(ofc_all_sing_regs, other_var_results_pres_short)

ofc_all_sing_regs <- left_join(ofc_all_sing_regs, pie_size_results_pres_short)

## not sig versions ##
not_sig_ofc_all_sing_regs <- left_join(ofc_non_sig_electrodes_of_interest, self_var_results_pres_short)

not_sig_ofc_all_sing_regs <- left_join(not_sig_ofc_all_sing_regs, other_var_results_pres_short)

not_sig_ofc_all_sing_regs <- left_join(not_sig_ofc_all_sing_regs, pie_size_results_pres_short)

```


```{r load-multiple-regs-dfs}

# load results for self var #
multiple_results_pres <- load_and_collate_reg_results(tag = "multiple-theta-pres-locked-hilbertRS", epoch = "presentation", folder = "post_eda/multiple_regressions")

# cut down variables #
multiple_results_pres <- multiple_results_pres  %>% mutate(type = "multiple")

# df for merging with single regs #
multiple_results_pres_short <- multiple_results_pres %>% 
  select(sub, electrode, perm_p, predictor) %>%
  distinct() %>%
  pivot_wider(names_from = predictor, values_from = perm_p)

```

```{r merge-mult-and-single-reg-dfs}
## sig versions ##
ofc_mult_and_single_df <- left_join(ofc_all_sing_regs, multiple_results_pres_short)

ofc_mult_and_single_table <- left_join(ofc_all_sing_regs %>% select(sub, electrode, predictor, perm_p, self_only, other_only, pie_size), multiple_results_pres_short) %>% distinct()

## no sig versions ##
not_sig_ofc_mult_and_single_df <- left_join(not_sig_ofc_all_sing_regs, multiple_results_pres_short)

not_sig_ofc_mult_and_single_table <- left_join(not_sig_ofc_all_sing_regs %>% select(sub, electrode, predictor, perm_p, self_only, other_only, pie_size), multiple_results_pres_short) %>% distinct()

```

## Significant Dis Inequity + Not Significant for Other or Self

```{r plot-betas-for-sig_dis-no-sig-other-self, warning=F}

for(sub_idx in unique(ofc_non_sig_electrodes_of_interest$sub)) {
  
  elecs_to_plot <- ofc_mult_and_single_table %>% filter(sub == sub_idx & self_only > 0.05 & other_only > 0.05) %>% pull(electrode)
  
  for(elec in unique(elecs_to_plot)) {

    multiple_results_pres_elec <- multiple_results_pres %>%
      filter(bin != "bin_37") %>%
      filter(sub == sub_idx & electrode == elec) %>%
      filter(predictor == "other_var_payoff_self_var_payoff") %>%
      mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
      mutate(Beta = Beta_1 - Beta_2)
    
    ofc_elec_of_interest <- ofc_electrodes_of_interest %>%
      filter(sub == sub_idx & electrode == elec) %>%
      mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
      mutate(sig_time = if_else(p < 0.05, time, -999)) %>%
      mutate(sig_time = replace(sig_time, sig_time == -999, NA))
    
    colors <- c("Dis. Ineq." = "#f9c74f", "Other - Self" = "#43aa8b", "Other, Mult. Reg" = "#f94144", "Self, Mult. Reg" = "#277da1")
    
    correlation <- round(cor(multiple_results_pres_elec$Beta, ofc_elec_of_interest$Beta), 2)
    
    p <- ggplot() +
      geom_point(data = ofc_elec_of_interest, aes(x = time, y = Beta, color = "Dis. Ineq.")) + # Yellow
      geom_line(data = ofc_elec_of_interest, aes(x = time, y = Beta, color = "Dis. Ineq.")) +
      geom_text(data = ofc_elec_of_interest, aes(x = sig_time), y = 0.032, label = "*", color = "black", size = 7) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta, color = "Other - Self")) + # green
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta, color = "Other - Self")) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta_1, color = "Other, Mult. Reg")) + # red, other
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta_1, color = "Other, Mult. Reg")) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta_2, color = "Self, Mult. Reg")) + # blue, self
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta_2, color = "Self, Mult. Reg")) +
      ylim(-0.032, 0.032) +
      labs(color = "Legend") +
      theme(panel.background = element_rect(fill = "white")) +
      scale_color_manual(values = colors) +
      ggtitle(paste(sub_idx, elec, correlation, sep = " ~ "))

    plot(p)
    
  } 
  
}  



```


## Significant Dis Inequity + Not Significant for Other or Self

```{r plot-betas-for-sig_dis, warning=F}

for(sub_idx in unique(ofc_non_sig_electrodes_of_interest$sub)) {
  
  elecs_to_plot <- ofc_mult_and_single_table %>% filter(sub == sub_idx & (self_only <= 0.05 | other_only <= 0.05)) %>% pull(electrode)
  
  for(elec in unique(elecs_to_plot)) {

    multiple_results_pres_elec <- multiple_results_pres %>%
      filter(bin != "bin_37") %>%
      filter(sub == sub_idx & electrode == elec) %>%
      filter(predictor == "other_var_payoff_self_var_payoff") %>%
      mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
      mutate(Beta = Beta_1 - Beta_2)
    
    ofc_elec_of_interest <- ofc_electrodes_of_interest %>%
      filter(sub == sub_idx & electrode == elec) %>%
      mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
      mutate(sig_time = if_else(p < 0.05, time, -999)) %>%
      mutate(sig_time = replace(sig_time, sig_time == -999, NA))
    
    correlation <- round(cor(multiple_results_pres_elec$Beta, ofc_elec_of_interest$Beta), 2)
    
    
    
    colors <- c("Dis. Ineq." = "#f9c74f", "Other - Self" = "#43aa8b", "Other, Mult. Reg" = "#f94144", "Self, Mult. Reg" = "#277da1")
    
    p <- ggplot() +
      geom_point(data = ofc_elec_of_interest, aes(x = time, y = Beta, color = "Dis. Ineq.")) + # Yellow
      geom_line(data = ofc_elec_of_interest, aes(x = time, y = Beta, color = "Dis. Ineq.")) +
      geom_text(data = ofc_elec_of_interest, aes(x = sig_time), y = 0.042, label = "*", color = "black", size = 7) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta, color = "Other - Self")) + # green
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta, color = "Other - Self")) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta_1, color = "Other, Mult. Reg")) + # red, other
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta_1, color = "Other, Mult. Reg")) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta_2, color = "Self, Mult. Reg")) + # blue, self
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta_2, color = "Self, Mult. Reg")) +
      ylim(-0.04, 0.042) +
      labs(color = "Legend") +
      theme(panel.background = element_rect(fill = "white")) +
      scale_color_manual(values = colors) +
      ggtitle(paste(sub_idx, elec, correlation, sep = " ~ "))

    plot(p)
    
  } 
  
}  



```

## Not sig versions ##

```{r non-sig-elecs}

for(sub_idx in unique(ofc_non_sig_electrodes_of_interest$sub)) {
  
  elecs_to_plot <- ofc_non_sig_electrodes_of_interest %>% filter(sub == sub_idx) %>% pull(electrode)
  
  for(elec in unique(elecs_to_plot)) {

      multiple_results_pres_elec <- multiple_results_pres %>%
        filter(bin != "bin_37") %>%
        filter(sub == sub_idx & electrode == elec) %>%
        filter(predictor == "other_var_payoff_self_var_payoff") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        mutate(Beta = Beta_1 - Beta_2)
      
      ofc_elec_of_interest <- ofc_non_sig_electrodes_of_interest %>%
        filter(sub == sub_idx & electrode == elec) %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) 
      
    correlation <- round(cor(multiple_results_pres_elec$Beta, ofc_elec_of_interest$Beta), 2)
      
    colors <- c("Dis. Ineq." = "#f9c74f", "Other - Self" = "#43aa8b", "Other, Mult. Reg" = "#f94144", "Self, Mult. Reg" = "#277da1")
    
    p <- ggplot() +
      geom_point(data = ofc_elec_of_interest, aes(x = time, y = Beta, color = "Dis. Ineq.")) + # Yellow
      geom_line(data = ofc_elec_of_interest, aes(x = time, y = Beta, color = "Dis. Ineq.")) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta, color = "Other - Self")) + # green
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta, color = "Other - Self")) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta_1, color = "Other, Mult. Reg")) + # red, other
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta_1, color = "Other, Mult. Reg")) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta_2, color = "Self, Mult. Reg")) + # blue, self
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta_2, color = "Self, Mult. Reg")) +
      ylim(-0.032, 0.032) +
      labs(color = "Legend") +
      theme(panel.background = element_rect(fill = "white")) +
      scale_color_manual(values = colors) +
      ggtitle(paste(sub_idx, elec, correlation, sep = " ~ "))

    plot(p)
      
  }

}


```



```{r ranadom, warning=F, eval = F}

tmp <- tmp %>%
  mutate(other_times_beta = other * -0.0063152950) %>%
  mutate(self_times_beta = self * 0.0086419716) %>%
  mutate(dis_ineq_times_mult_beta = dis * -0.0149572665 ) %>%
  mutate(dis_ineq_times_single_beta = dis * -0.014764410) %>%
  mutate(sum_other_and_self = other_times_beta + self_times_beta ) %>%
  mutate(sum_other_and_self_inter = sum_other_and_self -  dis_ineq_times_mult_beta)

brain_behave_data_elec %>%
  select(bin_13, ineq_disadvent, other_var_payoff, self_var_payoff) %>%
  gather(key = "regressor", value = "value", -bin_13) %>%
  # filter(regressor == "ineq_disadvent") %>%
  ggplot(., aes(x = value, y = bin_13, color = regressor, fill = regressor)) +
  geom_point() +
  geom_smooth() +
  theme(panel.background = element_rect(fill = "white"))

```

```{r csvs-dvoraah}

## stuff for Dvorah
 multiple_results_pres_elec <- multiple_results_pres %>%
        filter(sub == "IR28" & electrode == "LOF2-LOF3") %>%
        filter(predictor == "other_var_payoff_self_var_payoff") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        mutate(Beta = Beta_1 - Beta_2)
      
      ofc_elec_of_interest <- ofc_electrodes_of_interest %>%
        filter(sub == "IR28" & electrode == "LOF2-LOF3") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) 
      
write_csv(ofc_elec_of_interest, "IR28_LOF2-LOF3_ineq_disadvent_reg_results.csv")
write_csv(multiple_results_pres_elec, "IR28_LOF2-LOF3_other_var_self_var_multiple_reg_results.csv")

```


```{r clue-to-switch-frameworks-self_vvar_version}

 multiple_results_pres_elec <- multiple_results_pres %>%
        filter(bin != "bin_37") %>%
        filter(sub == "IR35" & electrode == "LOF3-LOF4") %>%
        filter(predictor == "ineq_disadvent_other_var_payoff") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        mutate(Beta = Beta_1 - Beta_2)
      
      ofc_elec_of_interest <- self_var_results_pres %>%
        filter(sub == "IR35" & electrode == "LOF3-LOF4" & predictor == "self_var_payoff") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) 
      
    
    # colors <- c("Dis. Ineq." = "#f9c74f", "Other - Self" = "#43aa8b", "Other, Mult. Reg" = "#f94144", "Self, Mult. Reg" = "#277da1")
    colors <- c("Self Var" = "#f9c74f", "Other, Mult. Reg" = "#f94144", "Dis Ineq, Mult. Reg" = "#277da1")
    
    p <- ggplot() +
      geom_point(data = ofc_elec_of_interest, aes(x = time, y = Beta, color = "Self Var")) + # Yellow
      geom_line(data = ofc_elec_of_interest, aes(x = time, y = Beta, color = "Self Var")) +
      # geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta, color = "Other - Self")) + # green
      # geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta, color = "Other - Self")) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta_1, color = "Dis Ineq, Mult. Reg")) + # red, other
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta_1, color = "Dis Ineq, Mult. Reg")) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta_2, color = "Other, Mult. Reg")) + # blue, self
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta_2, color = "Other, Mult. Reg")) +
      # ylim(-0.032, 0.032) +
      labs(color = "Legend") +
      theme(panel.background = element_rect(fill = "white")) +
      scale_color_manual(values = colors) +
      ggtitle(paste("IR35", "LOF3-LOF4", sep = " ~ "))

  plot(p)

```

```{r clue-to-switch-frameworks-self_var_dis_version, warning=F}

 multiple_results_pres_elec <- multiple_results_pres %>%
        filter(bin != "bin_37") %>%
        filter(sub == "IR35" & electrode == "LOF3-LOF4") %>%
        filter(predictor == "ineq_disadvent_other_var_payoff") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        mutate(Beta = Beta_1 - Beta_2) %>%
        mutate(sig_time = if_else(p_1 < 0.05, time, -999)) %>%
        mutate(sig_time = replace(sig_time, sig_time == -999, NA))
      
      ofc_elec_of_interest <- self_var_dis_results_pres %>%
        filter(sub == "IR35" & electrode == "LOF3-LOF4" & predictor == "self_var_payoff_dis") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) 
      
    
    # colors <- c("Dis. Ineq." = "#f9c74f", "Other - Self" = "#43aa8b", "Other, Mult. Reg" = "#f94144", "Self, Mult. Reg" = "#277da1")
    colors <- c("Self Var" = "#f9c74f", "Other, Mult. Reg" = "#f94144", "Dis Ineq, Mult. Reg" = "#277da1")
    
    p1 <- ggplot() +
      geom_point(data = ofc_elec_of_interest, aes(x = time, y = Beta, color = "Self Var")) + # Yellow
      geom_line(data = ofc_elec_of_interest, aes(x = time, y = Beta, color = "Self Var")) +
      geom_text(data = multiple_results_pres_elec, aes(x = sig_time), y = 0.045, label = "*", color = "black", size = 7) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta_1, color = "Dis Ineq, Mult. Reg")) + # red, other
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta_1, color = "Dis Ineq, Mult. Reg")) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = Beta_2, color = "Other, Mult. Reg")) + # blue, self
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = Beta_2, color = "Other, Mult. Reg")) +
      labs(color = "Legend") +
      theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
      scale_color_manual(values = colors) +
      ggtitle(paste("Betas", "IR35", "LOF3-LOF4", sep = " ~ "))


  
  colors_R2 <-  colors <- c("Self Var, Single Reg." = "grey", "Mult. Reg" = "black")
  p2 <- ggplot() +
      geom_point(data = ofc_elec_of_interest, aes(x = time, y = R2, color = "Self Var, Single Reg.")) + # Yellow
      geom_line(data = ofc_elec_of_interest, aes(x = time, y = R2, color = "Self Var, Single Reg.")) +
      geom_text(data = multiple_results_pres_elec, aes(x = sig_time), y = 0.045, label = "*", color = "black", size = 7) +
      geom_point(data = multiple_results_pres_elec, aes(x = time, y = R2, color = "Mult. Reg")) + # red, other
      geom_line(data = multiple_results_pres_elec, aes(x = time, y = R2, color = "Mult. Reg")) +
      labs(color = "Legend") +
      theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
      scale_color_manual(values = colors_R2) +
      ggtitle(paste("R2", "IR35", "LOF3-LOF4", sep = " ~ "))



plot(arrangeGrob(grobs = list(ggplotGrob(p1),ggplotGrob(p2)), nrow = 1, ncol = 2))

  
```

```{r diagnostics}

## read in data ##
path_hp_clean <- path(here(), "munge", "IR35", "theta_behave_presentation_rscaler_2575_200.csv")
power_behave <-  read.csv(path_hp_clean)

# add in new behavior vars #
brain_behave_data <- power_behave %>%
      filter(electrodes == "LOF3-LOF4") %>%
      mutate(pie_size = self_var_payoff + other_var_payoff) %>%
      mutate(self_var_payoff_adv = (as.numeric(other_var_payoff < self_var_payoff)) * self_var_payoff) %>%
      mutate(self_var_payoff_dis = (as.numeric(other_var_payoff > self_var_payoff)) * self_var_payoff) %>%
      mutate(other_var_payoff_adv = (as.numeric(other_var_payoff < self_var_payoff)) * other_var_payoff) %>%
      mutate(other_var_payoff_dis = (as.numeric(other_var_payoff > self_var_payoff)) * other_var_payoff)  


brain_behave_data %>%
  ggplot(., aes(y = bin_11, x = self_var_payoff_dis)) +
  geom_point() +
  geom_smooth() +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  ggtitle("self_var_payoff_dis")

brain_behave_data %>%
  ggplot(., aes(y = bin_11, x = ineq_disadvent)) +
  geom_point() +
  geom_smooth() +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  ggtitle("ineq_disadvent")


brain_behave_data %>%
  ggplot(., aes(y = bin_11, x = other_var_payoff)) +
  geom_point() +
  geom_smooth() +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  ggtitle("other_var_payoff")


model_2 <- lm(bin_11 ~ ineq_disadvent + other_var_payoff, data = brain_behave_data)
summary(model_2)


brain_behave_data %>%
  mutate(y_pred = 0.04338 * ineq_disadvent + -0.04177 * other_var_payoff) %>%
  ggplot(., aes(y = bin_11, x = y_pred)) +
  geom_point() +
  geom_smooth() +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  ggtitle("model prediction")


brain_behave_data %>%
  filter(ineq_disadvent != 0) %>%
  ggplot(., aes(y = bin_11, x = ineq_disadvent)) +
  geom_point() +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  ggtitle("ineq_disadvent no zeroes")


```


```{r pie-siz}

## plots with pie size ##

hold <- multiple_results_pres %>% filter(sub == "IR28" & electrode == "LOF2-LOF3" & predictor == "other_var_payoff_self_var_payoff")
hold2 <- pie_size_results_pres %>% filter(sub == "IR28" & electrode == "LOF2-LOF3")

pie_size <- rbind(hold %>% select(bin, R2, type), hold2 %>% select(bin, R2, type))

ggthemr("light")
pie_size %>%
  mutate(model = replace(type, type == "single", "Pie Size")) %>%
  mutate(model = replace(model, type == "multiple", "Other - Self")) %>%
  mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
  ggplot(., aes(x = time, y = R2, color = model)) +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) 

hold <- hold %>% select(bin, Beta_1, Beta_2)  %>% gather(key = "tmp", value = "Beta", -bin) %>% rename(type = tmp)
pie_size <- rbind(hold %>% select(bin, Beta, type), hold2 %>% select(bin, Beta, type))

pie_size %>%
  mutate(model = replace(type, type == "single", "Pie Size")) %>%
  mutate(model = replace(model, type == "Beta_1", "Other")) %>%
  mutate(model = replace(model, type == "Beta_2", "Self")) %>%
  mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
  distinct() %>%
  ggplot(., aes(x = time, y = Beta, color = model)) +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) 

```

### Trial Type Models

```{r trial-types}

# add in anatomy #
trial_type_localized_results_pres <- merge_all_subs_with_elec_info(trial_type_results_pres, localizations)

# cut to ofc #
ofc_trial_type_results_pres <- trial_type_localized_results_pres %>% filter(grepl("ofc", ROI, ignore.case = T) | grepl("orbit", ROI, ignore.case = T))

ofc_trial_type_results_pres %>%
    select(perm_p, sub, electrode) %>%
    mutate(sig = perm_p < 0.05) %>%
    distinct() %>%
    add_count(sig) %>%
    select(n, sig) %>%
    distinct() %>%
    kable(caption = name) %>%
    kable_styling()


trial_plot <- ofc_trial_type_results_pres %>%
  filter(perm_p < 0.5) %>%
  mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
  mutate(sub_elec = paste(sub, electrode, sep = "_")) %>%
  mutate(sig_time = if_else(p < 0.05, time, -999)) %>%
  mutate(sig_time = replace(sig_time, sig_time == -999, NA)) %>%
  ggplot(., aes(x = time, y = R2, color = electrode)) +
  geom_text(aes(x = sig_time, color = electrode), y = 0.045, label = "*", size = 7) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = getPalette(7)) +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  facet_wrap(~sub) +
  ggtitle("Trial Type")


plot(arrangeGrob(grobs = list(ggplotGrob(trial_plot),ggplotGrob(p_self)), nrow = 1, ncol = 2))


```


electrodes that encode self, some that encode, other and some that do both

```{r diagnose-models}

# add in new behavior vars #
brain_behave_data_trial <- power_behave %>%
  filter(electrodes == "LOF1-LOF2") %>%
  mutate(trial_type = if_else(self_var_payoff == other_var_payoff, "equality",
                            if_else(self_var_payoff > other_var_payoff,
                                    "Advantageous", "Disadvantageous"))) %>%
  filter(trial_type != "equality") %>%
  group_by(trial_type) %>%
  mutate(mean_bin = mean(bin_24)) %>%
  select(bin_24, trial_type, mean_bin)

brain_behave_data_trial %>%  
  ggplot(., aes(x = trial_type, y = bin_24)) +
  geom_point() +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
                 width = .3, color = "black") +
  theme(panel.background = element_rect(fill = "white"))

summary(lm(bin_24 ~ trial_type, data = brain_behave_data_trial))

```


### self var models 

```{r trial-types}

# add in anatomy #
self_var_localized_results_pres <- merge_all_subs_with_elec_info(self_var_results_pres, localizations)

# cut to ofc #
ofc_self_var_results_pres <- self_var_localized_results_pres %>% filter(grepl("ofc", ROI, ignore.case = T) | grepl("orbit", ROI, ignore.case = T))

ofc_self_var_results_pres %>%
    select(perm_p, sub, electrode) %>%
    mutate(sig = perm_p < 0.05) %>%
    distinct() %>%
    add_count(sig) %>%
    select(n, sig) %>%
    distinct() %>%
    kable(caption = name) %>%
    kable_styling()


p_self <- ofc_self_var_results_pres %>%
  filter(perm_p < 0.5) %>%
  mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
  mutate(sub_elec = paste(sub, electrode, sep = "_")) %>%
  mutate(sig_time = if_else(p < 0.05, time, -999)) %>%
  mutate(sig_time = replace(sig_time, sig_time == -999, NA)) %>%
  ggplot(., aes(x = time, y = R2, color = electrode)) +
  geom_text(aes(x = sig_time, color = electrode), y = 0.045, label = "*", size = 7) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = getPalette(7)) +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  facet_wrap(~sub) +
  ggtitle("Self Var Payoff")


```

### other var models 

```{r other-var, warning = F}

freq_bands <- c("hfa")

for(freq in freq_bands) {

  # load results for self var #
  other_var_results_pres <- load_and_collate_reg_results(tag = paste0("other_var_payoff_", freq, "-pres-locked-hilbertRS"), epoch = "presentation", folder = "post_eda")
  
  # change predictor #
  other_var_results_pres <- other_var_results_pres %>% mutate(predictor = "other_var_payoff") %>% mutate(type = "single")
  
  
  # add in anatomy #
  other_var_localized_results_pres <- merge_all_subs_with_elec_info(other_var_results_pres, localizations)
  
  # cut to ofc #
  ofc_other_var_results_pres <- other_var_localized_results_pres %>% filter(grepl("ofc", ROI, ignore.case = T) | grepl("orbit", ROI, ignore.case = T))
  
  table <- ofc_other_var_results_pres %>%
      select(perm_p, sub, electrode) %>%
      mutate(sig = perm_p < 0.05) %>%
      distinct() %>%
      add_count(sig) %>%
      select(n, sig) %>%
      distinct() %>%
      kable(caption = name) %>%
      kable_styling()
  
  plot(table)
  
  
  p <- ofc_other_var_results_pres %>%
    filter(perm_p < 0.5) %>%
    mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
    mutate(sub_elec = paste(sub, electrode, sep = "_")) %>%
    mutate(sig_time = if_else(p < 0.05, time, -999)) %>%
    mutate(sig_time = replace(sig_time, sig_time == -999, NA)) %>%
    ggplot(., aes(x = time, y = R2, color = electrode)) +
    geom_text(aes(x = sig_time, color = electrode), y = 0.045, label = "*", size = 7) +
    geom_line() +
    geom_point() +
    ylim(0, 0.046) +
    scale_color_manual(values = getPalette(7)) +
    theme(panel.background = element_rect(fill = "white")) +
    facet_wrap(~sub) +
    ggtitle(paste0("Other Var Payoff", freq, sep = " ~ "))
  
  plot(p)

}


```
### pie size

```{r pie-size, warning=F}

# add in anatomy #
pie_size_localized_results_pres <- merge_all_subs_with_elec_info(pie_size_results_pres, localizations)

# cut to ofc #
ofc_pie_size_results_pres <- pie_size_localized_results_pres %>% filter(grepl("ofc", ROI, ignore.case = T) | grepl("orbit", ROI, ignore.case = T))

ofc_pie_size_results_pres %>%
    select(perm_p, sub, electrode) %>%
    mutate(sig = perm_p < 0.05) %>%
    distinct() %>%
    add_count(sig) %>%
    select(n, sig) %>%
    distinct() %>%
    kable(caption = name) %>%
    kable_styling()


ofc_pie_size_results_pres %>%
  filter(perm_p < 0.5) %>%
  mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
  mutate(sub_elec = paste(sub, electrode, sep = "_")) %>%
  mutate(sig_time = if_else(p < 0.05, time, -999)) %>%
  mutate(sig_time = replace(sig_time, sig_time == -999, NA)) %>%
  ggplot(., aes(x = time, y = R2, color = electrode)) +
  geom_text(aes(x = sig_time, color = electrode), y = 0.03, label = "*", size = 7) +
  geom_line() +
  geom_point() +
  ylim(0, 0.032) +
  scale_color_manual(values = getPalette(7)) +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~sub) +
  ggtitle("Pie Size")


```


### Interaction Models


```{r load_interaction-data}

delta_pres_inter_reg_results <- load_interaction_results_and_combine(epoch = "presentation", freq = "delta", pred = "self_var_payoff_less_or_none")
theta_pres_inter_reg_results <- load_interaction_results_and_combine(epoch = "presentation", freq = "theta", pred = "self_var_payoff_less_or_none")
alpha_pres_inter_reg_results <- load_interaction_results_and_combine(epoch = "presentation", freq = "alpha", pred = "self_var_payoff_less_or_none")
gamma_pres_inter_reg_results <- load_interaction_results_and_combine(epoch = "presentation", freq = "gamma", pred = "self_var_payoff_less_or_none")
beta_pres_inter_reg_results <- load_interaction_results_and_combine(epoch = "presentation", freq = "beta", pred = "self_var_payoff_less_or_none")
hfaa_pres_inter_reg_results <- load_interaction_results_and_combine(epoch = "presentation", freq = "hfa", pred = "self_var_payoff_less_or_none")


feqs_df <- list(delta_pres_inter_reg_results %>% mutate(freq = "delta"), 
                theta_pres_inter_reg_results %>% mutate(freq = "theta"), 
                alpha_pres_inter_reg_results %>% mutate(freq = "alpha"), 
                beta_pres_inter_reg_results %>% mutate(freq = "beta"),
                gamma_pres_inter_reg_results %>% mutate(freq = "gamma"),
                hfaa_pres_inter_reg_results %>% mutate(freq = "hfa"))

# print tables #
for(df in feqs_df) {
  
  ofc_df_pres_inter_reg_results <-  df %>% filter(grepl("ofc", ROI, ignore.case = T) | grepl("orbit", ROI, ignore.case = T))
  
  name <- paste("OFC Results", unique(ofc_df_pres_inter_reg_results$freq), sep = " ~ ")
  
 table <- ofc_df_pres_inter_reg_results %>%
    select(perm_p, sub, electrode) %>%
    mutate(sig = perm_p < 0.05) %>%
    distinct() %>%
    add_count(sig) %>%
    select(n, sig) %>%
    distinct() %>%
    kable(caption = name) %>%
    kable_styling()
 
 print(table)

}

# get elecs #
sig_ofc_inter_elecs <- NA
for(df in feqs_df) {
  
  ofc_df_pres_inter_reg_results <-  df %>% filter(grepl("ofc", ROI, ignore.case = T) | grepl("orbit", ROI, ignore.case = T))
  
  
 tmp_df <- ofc_df_pres_inter_reg_results %>%
    select(perm_p, sub, electrode, freq) %>%
    filter(perm_p < 0.05) %>%
    distinct()
    
 
 if(is.na(sig_ofc_inter_elecs)) {
   sig_ofc_inter_elecs <- tmp_df
 } else(
   sig_ofc_inter_elecs <- rbind(sig_ofc_inter_elecs, tmp_df)
 )

}

sig_ofc_inter_elecs %>%
  pivot_wider(names_from = freq, values_from = perm_p) %>%
  kable() %>%
  kable_styling()

```


### subject specific ##

```{r IR10}

IR10_self_var_results_pres <- self_var_localized_results_pres %>%
  filter(sub == "IR10") %>%
  filter(grepl("ofc", ROI, ignore.case = T) | grepl("orbit", ROI, ignore.case = T)) %>%
  mutate(sig = perm_p < 0.05)


# IR10 doesn't have OFC electrodes!

```

```{r IR26}

IR26_self_var_results_pres <- self_var_localized_results_pres %>%
  filter(sub == "IR26") %>%
  filter(grepl("ofc", ROI, ignore.case = T) | grepl("orbit", ROI, ignore.case = T)) %>%
  mutate(sig = perm_p < 0.05)


# IR26 has 3 OFC electrodes, but none are sig!

```

