---
title: "Visualize Results"
author: "Brooke Staveland"
date: "4/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo <- FALSE,  # don't print the code chunk
  warning <- FALSE,  # don't print warnings
  message <- FALSE,  # don't print messages
  fig.width <- 12,  # set default width of figures
  fig.height <- 6,  # set default height of figures
  fig.align <- "center",  # always align figure in center
  fig.pos <- "H",  # always plot figure at the exact location of the code chunk
  cache <- TRUE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
# library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)

## hand written functions ##
source(path(here(), "R", "load_behave_data.R"))
source(path(here(), "R", "prep_behave_data.R"))
source(path(here(), "R", "stretch_start_end.R"))
source(path(here(), "R", "load_high_gamma_data.R"))
source(path(here(), "R", "rolling_window_and_baseline.R"))
source(path(here(), "R", "run_permuted_regressions.R"))
source(path(here(), "R", "compile_results.R"))
source(path(here(), "R", "run_filtered_anova.R"))
source(path(here(), "R", "merge_stepped_anova_results.R"))
# source('~/Projects/nice_r_functions/ggpaired_pretty.R')
source(path(here(), "R", 'mutate_cond.R'))

## plotting helpers ##
# ggthemr("solarized")

## paralellization ##
nCores <- 2
registerDoParallel(nCores)

```

# Dictator Game Regression Results

This analysis script visualizes the output of the permuted regressions.

## Load Presentation

Load and prep presentation-locked results for all subjects.

```{r concatenate-results-presentation}

## IR39 ##

# combine different csvs #
regions_to_combine <- c("Insula")
presentation_results_39 <- compile_results(regions_to_combine, type = "pres-locked-100", sub = "IR39", path = path(here(), "results", "IR39", "insula"), absBeta = T)

# runa anova for inequity results #
path_hg_clean <- path(here(), "munge", "IR39", "hg_behave_presentation_locked_extended_100_insula.csv")
# hg_behave <-  read.csv(path_hg_clean)
# run_filtered_anova(presentation_results_39, hg_behave, sub = "IR39", region_name = "All", all_results = T, type = "pres-locked_insula")

# read back in the results #
region_name <- "All"
adv_pres_results_for_plots_39 <- read.csv(fs::path(here(), "results", "IR39", paste0(region_name, "_pres-locked_insula_anova_results_advantageous.csv")))
dis_pres_results_for_plots_39 <- read.csv(fs::path(here(), "results", "IR39", paste0(region_name, "_pres-locked_anova_results_disadvantageous.csv")))


## IR35 ##

# combine different csvs #
regions_to_combine <- c("Insula")
presentation_results_35 <- compile_results(regions_to_combine, type = "pres-locked", sub = "IR35", path = path(here(), "results", "IR35", "insula"), absBeta = T)

# runa anova for inequity results #
path_hg_clean <- path(here(), "munge", "IR35", "hg_behave_presentation_locked_extended_150_insula.csv")
hg_behave <-  read.csv(path_hg_clean)
run_filtered_anova(presentation_results_35, hg_behave, sub = "IR35", region_name = "All", all_results = T, type = "pres-locked_insula")

# read back in the results #
region_name <- "All"
adv_pres_results_for_plots_35 <- read.csv(fs::path(here(), "results", "IR35", paste0(region_name, "_pres-locked_insula_anova_results_advantageous.csv")))
dis_pres_results_for_plots_35 <- read.csv(fs::path(here(), "results", "IR35", paste0(region_name, "_pres-locked_insula_anova_results_disadvantageous.csv")))

## IR19 ##

# combine different csvs #
regions_to_combine <- c("Insula")
presentation_results_19 <- compile_results(regions_to_combine, type = "pres-locked", sub = "IR19", path = path(here(), "results", "IR19", "insula"), absBeta = T)

# runa anova for inequity results #
path_hg_clean <- path(here(), "munge", "IR19", "hg_behave_presentation_locked_extended_150_insula.csv")
hg_behave <-  read.csv(path_hg_clean)
hg_behave <- hg_behave %>% mutate(electrodes = gsub("POL ", "", electrodes)) # IR19 has weird elec names
# run_filtered_anova(presentation_results_19, hg_behave, sub = "IR19", region_name = "All", all_results = T, type = "pres-locked_insula")

# read back in the results #
region_name <- "All"
adv_pres_results_for_plots_19 <- read.csv(fs::path(here(), "results", "IR19", paste0(region_name, "_pres-locked_insula_anova_results_advantageous.csv")))
dis_pres_results_for_plots_19 <- read.csv(fs::path(here(), "results", "IR19", paste0(region_name, "_pres-locked_insula_anova_results_disadvantageous.csv")))

```

## Load Choice

Load and prep choice-locked results for all subjects.


```{r concatenate-results-choice}


## IR39 ##

# combine different csvs #
regions_to_combine <- c("Insula")
choice_results_39 <- compile_results(regions_to_combine, type = "choice-locked", sub = "IR39", path = path(here(), "results", "IR39", "insula"), absBeta = T)

# runa anova for inequity results #
path_hg_clean <- path(here(), "munge", "IR39", "hg_behave_choice_locked_cut_fixation_150_insula.csv")
# hg_behave <-  read.csv(path_hg_clean)
# run_filtered_anova(choice_results_39, hg_behave, sub = "IR39", region_name = "All", all_results = T, type = "choice-locked_insula")

# read back in the results #
region_name <- "All"
adv_choice_results_for_plots_39 <- read.csv(fs::path(here(), "results", "IR39", paste0(region_name, "_choice-locked_insula_anova_results_advantageous.csv")))
dis_choice_results_for_plots_39 <- read.csv(fs::path(here(), "results", "IR39", paste0(region_name, "_choice-locked_insula_anova_results_disadvantageous.csv")))


## IR35 ##

# combine different csvs #
regions_to_combine <- c("Insula")
choice_results_35 <- compile_results(regions_to_combine, type = "choice-locked", sub = "IR35", path = path(here(), "results", "IR35", "insula"), absBeta = T)

# runa anova for inequity results #
path_hg_clean <- path(here(), "munge", "IR35", "hg_behave_choice_locked_cut_fixation_150_insula.csv")
# hg_behave <-  read.csv(path_hg_clean)
# run_filtered_anova(choice_results_35, hg_behave, sub = "IR35", region_name = "All", all_results = T, type = "choice-locked_insula")

# read back in the results #
region_name <- "All"
adv_choice_results_for_plots_35 <- read.csv(fs::path(here(), "results", "IR35", paste0(region_name, "_choice-locked_insula_anova_results_advantageous.csv")))
dis_choice_results_for_plots_35 <- read.csv(fs::path(here(), "results", "IR35", paste0(region_name, "_choice-locked_insula_anova_results_disadvantageous.csv")))

## IR19 ##

# combine different csvs #
regions_to_combine <- c("Insula")
choice_results_19 <- compile_results(regions_to_combine, type = "choice-locked", sub = "IR19", path = path(here(), "results", "IR19", "insula"), absBeta = T)

# runa anova for inequity results #
path_hg_clean <- path(here(), "munge", "IR19", "hg_behave_choice_locked_cut_fixation_150_insula.csv")
# hg_behave <-  read.csv(path_hg_clean)
# hg_behave <- hg_behave %>% mutate(electrodes = gsub("POL ", "", electrodes)) # IR19 has weird elec names
# run_filtered_anova(choice_results_19, hg_behave, sub = "IR19", region_name = "All", all_results = T, type = "choice-locked_insula")

# read back in the results #
region_name <- "All"
adv_choice_results_for_plots_19 <- read.csv(fs::path(here(), "results", "IR19", paste0(region_name, "_choice-locked_insula_anova_results_advantageous.csv")))
dis_choice_results_for_plots_19 <- read.csv(fs::path(here(), "results", "IR19", paste0(region_name, "_choice-locked_insula_anova_results_disadvantageous.csv")))


```

## plotting functions

```{r plotting-functions}
ggthemr::ggthemr("pale", layout = "plain")
getPalette = colorRampPalette(brewer.pal(8, "Set1"))

ineq_plots <- function(df, title) {
# plots the bar plots of dif in R2 for inequity  
df %>%
    ungroup() %>%
    mutate(sig = if_else(perm_p < 0.05 & anova_p < 0.01, "Significant", "Insignificant")) %>%
    mutate_cond(sig == "Significant", sig = as.character(region)) %>%
    mutate(sig = relevel(factor(sig), ref = "Insignificant")) %>%
    # mutate(bin = factor(bin, levels = colnames(hg_data)[4:38])) %>%
    ggplot(., aes( x = bin, y = diff_adj_r2, color = sig, fill = sig)) +
    geom_col(alpha = .5) +
    # geom_vline(aes(xintercept = which(levels(bin) %in% "post_1"))) +
    theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.background = element_rect(fill = "white")) + 
    scale_fill_manual(values = c("grey", getPalette(4))) +
    scale_color_manual(values = c("grey", getPalette(4))) +
    labs(y = "Difference in Adj. R Squared", x = "Bins", fill = "Region", color = "Region") +
    facet_wrap(~electrode) + 
    ggtitle(title)
  
}

active_elec_plots <- function(df, var, title) {
  df %>%
    filter(predictor == var) %>%
    mutate(sig = if_else(perm_p < 0.0125 & p < 0.05, "Significant", "Insignificant")) %>%
    mutate_cond(sig == "Significant", sig = as.character(region)) %>%
    mutate(sig = relevel(factor(sig), ref = "Insignificant")) %>%
    # mutate(bin = factor(bin, levels = colnames(hg_data)[4:38])) %>%
    ggplot(., aes( x = bin, y = R2, color = sig, fill = sig)) +
    geom_col(alpha = .5) +
    # geom_vline(aes(xintercept = which(levels(bin) %in% "post_1"))) +
    theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.background = element_rect(fill = "white")) + 
    scale_fill_manual(values = c("grey", getPalette(4))) +
    scale_color_manual(values = c("grey", getPalette(4))) +
    labs(y = "Adj. R Squared", x = "Bins", fill = "Region", color = "Region") +
    facet_wrap(~electrode) + 
    ggtitle(title)

}

combined_active_plots <- function(df, subject, num_rows, sig_thresh){
  df  %>%
    # filter(!predictor %in% c("ineq_advent", "ineq_disadvent")) %>%
    mutate(bin_sig = if_else((p < .05 & perm_p < 0.0125), 1, 0)) %>%
    mutate(Beta = if_else(predictor == "ineq_advent", Beta * -1, Beta)) %>%
    mutate(bin_sig = if_else(Beta < 0 & bin_sig == 1, -1, bin_sig)) %>%
    group_by(bin, electrode) %>%
    mutate(bin_sum = sum(bin_sig)/6) %>%
    ungroup() %>%
    mutate(predictor = if_else(bin_sig == 0, "Insig", as.character(predictor))) %>%
    mutate(predictor = relevel(factor(predictor), ref = "Insig")) %>%
    mutate(bin = as.numeric(gsub("bin_", "", bin))) %>%
    arrange(bin) %>%
    ggplot(., aes(x= bin, y = bin_sig, fill = predictor, color = predictor)) + 
    geom_col(alpha = .5) + 
    theme(axis.text.x = element_text(angle = 90),
          # axis.ticks.x = element_blank(),
          panel.background = element_rect(fill = "white")) +
      scale_fill_manual(values = c("grey", getPalette(8))) +
      scale_color_manual(values = c("grey", getPalette(8))) +
      labs(y = "number of sig. predictors", x = "Bins", fill = "Region", color = "Region") +
    facet_wrap(~electrode, nrow = num_rows) +
    ggtitle(paste0(subject, " ~ thresh @ ", sig_thresh))
}


combined_beta_plots <- function(df, subject, num_rows, sig_thresh){
  df  %>%
    # filter(!predictor %in% c("ineq_advent", "ineq_disadvent")) %>%
    mutate(bin_sig = if_else((p < .05 & perm_p < sig_thresh), 1, 0)) %>%
    mutate(Beta = if_else(predictor == "ineq_advent", Beta * -1, Beta)) %>%
    mutate(bin_sig = if_else(Beta < 0 & bin_sig == 1, -1, bin_sig)) %>%
    group_by(bin, electrode) %>%
    mutate(bin_sum = sum(bin_sig)/6) %>%
    ungroup() %>%
    mutate(predictor_insig = if_else(bin_sig == 0, "Insig", as.character(predictor))) %>%
    mutate(predictor_insig = relevel(factor(predictor_insig), ref = "Insig")) %>%
    mutate(bin = as.numeric(gsub("bin_", "", bin))) %>%
    arrange(bin) %>%
    ggplot(., aes(x= bin, y = Beta, group = predictor, fill = predictor_insig, color = predictor_insig)) + 
    geom_point(alpha = .5) + 
    geom_line() +
    theme(axis.text.x = element_text(angle = 90),
          # axis.ticks.x = element_blank(),
          panel.background = element_rect(fill = "white")) +
      scale_fill_manual(values = c("grey", getPalette(8))) +
      scale_color_manual(values = c("grey", getPalette(8))) +
      labs(y = "number of sig. predictors", x = "Bins", fill = "Region", color = "Region") +
    facet_wrap(~electrode, nrow = num_rows) +
    ggtitle(paste0(subject, " ~ thresh @ ", sig_thresh))
}

combined_active_plots_choice <- function(df, subject, num_rows, sig_thresh){
  df  %>%
    # filter(!predictor %in% c("ineq_advent", "ineq_disadvent")) %>%
    mutate(bin_sig = if_else((p < .05 & perm_p < 0.0125), 1, 0)) %>%
    mutate(Beta = if_else(predictor == "ineq_advent", Beta * -1, Beta)) %>%
    mutate(bin_sig = if_else(Beta < 0 & bin_sig == 1, -1, bin_sig)) %>%
    group_by(bin, electrode) %>%
    mutate(bin_sum = sum(bin_sig)/6) %>%
    ungroup() %>%
    mutate(predictor = if_else(bin_sig == 0, "Insig", as.character(predictor))) %>%
    mutate(predictor = relevel(factor(predictor), ref = "Insig")) %>%
    mutate(bin = gsub("pre_", "-", bin)) %>%
    mutate(bin = as.numeric(gsub("post_", "", bin))) %>%
    arrange(bin) %>%
    ggplot(., aes(x= bin, y = bin_sig, fill = predictor, color = predictor)) + 
    geom_col(alpha = .5) + 
    geom_vline(xintercept = 0, color = "black") +
    theme(axis.text.x = element_text(angle = 90),
          # axis.ticks.x = element_blank(),
          panel.background = element_rect(fill = "white")) +
      scale_fill_manual(values = c("grey", getPalette(8))) +
      scale_color_manual(values = c("grey", getPalette(8))) +
      labs(y = "number of sig. predictors", x = "Bins", fill = "Region", color = "Region") +
    facet_wrap(~electrode, nrow = num_rows) +
    ggtitle(paste0(subject, " ~ thresh @ ", sig_thresh))
}

```

## Presentation Results

```{r presentation-results}

## exclude mistaken regions!! ###
presentation_results_35 <- presentation_results_35 %>% filter(electrode != "LAC10-LAC11" & electrode != "LAC9-LAC10" & electrode != "LIN9-LIN10")
presentation_results_19 <- presentation_results_19 %>% filter(electrode != "LIN10-Ref-LIN11-Ref" & electrode != "LIN12-Ref-LIN13-Ref" & electrode != "LIN11-Ref-LIN12-Ref" & electrode != "LIN9-Ref-LIN10-Ref" & electrode != "RIN10-Ref-RIN11-Ref" & electrode != "RIN11-Ref-RIN12-Ref" & electrode != "RIN12-Ref-RIN13-Ref" & electrode != "RIN9-Ref-RIN10-Ref")

plot_39_00625 <- combined_active_plots(presentation_results_39, "IR39 ~ Presentation", 2, sig_thresh = 0.00625)
plot_35_00625 <- combined_active_plots(presentation_results_35, "IR35 ~ Presentation", 2, sig_thresh = 0.00625)
plot_19_00625 <- combined_active_plots(presentation_results_19, "IR19 ~ Presentation", 3, sig_thresh = 0.00625)

ggsave(filename = paste0(path(here(), './figures/plot_39_00625.png')),
     device = "png",
     width = 20,
     height = 10,
     units = "cm",
     dpi = 200,
     plot =  print(plot(plot_39_00625)) )

ggsave(filename = paste0(path(here(), './figures/plot_35_00625.png')),
     device = "png",
     width = 20,
     height = 10,
     units = "cm",
     dpi = 200,
     plot =  print(plot(plot_35_00625)) )

ggsave(filename = paste0(path(here(), './figures/plot_19_00625.png')),
     device = "png",
     width = 20,
     height = 10,
     units = "cm",
     dpi = 200,
     plot =  print(plot(plot_19_00625)) )

```

## Choice Resutls

```{r choice_results}

getPalette = colorRampPalette(brewer.pal(8, "Set1"))


## exclude mistaken regions!! ###
choice_results_35 <- choice_results_35 %>% filter(electrode != "LAC10-LAC11" & electrode != "LAC9-LAC10" & electrode != "LIN9-LIN10")
choice_results_19 <- choice_results_19 %>% filter(electrode != "LIN10-Ref-LIN11-Ref" & electrode != "LIN12-Ref-LIN13-Ref" & electrode != "LIN11-Ref-LIN12-Ref" & electrode != "LIN9-Ref-LIN10-Ref" & electrode != "RIN10-Ref-RIN11-Ref" & electrode != "RIN11-Ref-RIN12-Ref" & electrode != "RIN12-Ref-RIN13-Ref" & electrode != "RIN9-Ref-RIN10-Ref")


## plot it ##

combined_active_plots_choice(choice_results_39, "IR39-Choice", 2)
combined_active_plots_choice(choice_results_35, "IR35-Choice", 2)
combined_active_plots_choice(choice_results_19, "IR19-Choice", 3)


```


## Inequity Results

### Presentation

Summary:
* IR34
 - Lin-3-4, adv, blue/green
* IR39
 - Lin-1-2, dis, blue
 - Lof-5-6, dis, purple
 - Rin-1-2, dis, green/blue
* IR19
 - Rin-1-2, adv, blue/green
 - Rin-1-2, dis, blue/green
 - Rin-1-2, dis, blue/green
 


```{r inequity-pres}

## remove sneaky electrodes
adv_pres_results_for_plots_35 <- adv_pres_results_for_plots_35 %>% filter(electrode != "LAC10-LAC11" & electrode != "LAC9-LAC10" & electrode != "LIN9-LIN10")
dis_pres_results_for_plots_35 <- dis_pres_results_for_plots_35 %>% filter(electrode != "LAC10-LAC11" & electrode != "LAC9-LAC10" & electrode != "LIN9-LIN10")

adv_pres_results_for_plots_19 <- adv_pres_results_for_plots_19 %>% filter(electrode != "LIN10-Ref-LIN11-Ref" & electrode != "LIN12-Ref-LIN13-Ref" & electrode != "LIN11-Ref-LIN12-Ref" & electrode != "LIN9-Ref-LIN10-Ref" & electrode != "RIN10-Ref-RIN11-Ref" & electrode != "RIN11-Ref-RIN12-Ref" & electrode != "RIN12-Ref-RIN13-Ref" & electrode != "RIN9-Ref-RIN10-Ref")
dis_pres_results_for_plots_19 <- dis_pres_results_for_plots_19 %>% filter(electrode != "LIN10-Ref-LIN11-Ref" & electrode != "LIN12-Ref-LIN13-Ref" & electrode != "LIN11-Ref-LIN12-Ref" & electrode != "LIN9-Ref-LIN10-Ref" & electrode != "RIN10-Ref-RIN11-Ref" & electrode != "RIN11-Ref-RIN12-Ref" & electrode != "RIN12-Ref-RIN13-Ref" & electrode != "RIN9-Ref-RIN10-Ref")


## Presentation ##

ineq_plots(adv_pres_results_for_plots_35, "Advantageous Inequality Results: IR35")
ineq_plots(dis_pres_results_for_plots_35, "Disdvantageous Inequality Results: IR35")

ineq_plots(adv_pres_results_for_plots_39, "Advantageous Inequality Results: IR39")
ineq_plots(dis_pres_results_for_plots_39, "Disdvantageous Inequality Results: IR39")

ineq_plots(adv_pres_results_for_plots_19, "Advantageous Inequality Results: IR19")
ineq_plots(dis_pres_results_for_plots_19, "Disdvantageous Inequality Results: IR19")


```


### Choice

```{r inequity-choice}
## Presentation ##

ineq_plots(adv_choice_results_for_plots_35, "Advantageous Inequality Results: IR35")
ineq_plots(dis_choice_results_for_plots_35, "Disdvantageous Inequality Results: IR35")

ineq_plots(adv_choice_results_for_plots_39, "Advantageous Inequality Results: IR39")
ineq_plots(dis_choice_results_for_plots_39, "Disdvantageous Inequality Results: IR39")

ineq_plots(adv_choice_results_for_plots_19, "Advantageous Inequality Results: IR19")
ineq_plots(dis_choice_results_for_plots_19, "Disdvantageous Inequality Results: IR19")

```

